# RESULTS

## FISHING OPERATIONS
```{r fishing}

coastaltows <- bridgetow %>%
  filter(`Trawl Net` == "LFS 7742") %>%
  nrow

offshoretows <- bridgetow %>%
  filter(`Trawl Net` == "LFS 1142") %>%
  nrow

offshorehigh <- bridgetow %>%
  filter(Usable == "Y" & `Trawl Net` == "LFS 1142") %>%
  pull(`Net Opening Height (m)`) %>%
  mean %>%
  round()

offshorewide <- bridgetow %>%
  filter(Usable == "Y" & `Trawl Net` == "LFS 1142") %>%
  pull(`Net Opening Width (m)`) %>%
  mean %>%
  round()

coastalhigh <- bridgetow %>%
  filter(Usable == "Y" & `Trawl Net` == "LFS 7742") %>%
  pull(`Net Opening Height (m)`) %>%
  mean %>%
  round()

coastalwide <- bridgetow %>%
  filter(Usable == "Y" & `Trawl Net` == "LFS 7742") %>%
  pull(`Net Opening Width (m)`) %>%
  mean %>%
  round()

```

This survey completed `r offshoretows` offshore LFS 1142 trawl net tows for gear setup (4 with the codend open; 2 with the codend closed) and `r coastaltows` coastal LFS 7742 trawl net tows (Appendix \@ref(app:appBridge)). Although four offshore LFS 1142 trawl net adjustment tows were done with the codend open to avoid the capture of fish, a 4.6 m male Common Thresher Shark (*Alopias vulpinus*) was captured, and released alive from the first tow (Figure \@ref(fig:sharkphoto)). The last coastal LFS 7742 trawl net tow of the survey was aborted in Queen Charlotte Strait due to equipment failure of the third wire winch. Subsequent tows were cancelled.

The offshore LFS 1142 mouth opening averaged `r offshorehigh` m high by `r offshorewide` m wide, or an area of `r round(offshorehigh * offshorewide)` m^2^. This opening is slightly smaller than to the expected net area opening of 30 m high by 46 m wide, or an area of 1380 m^2^ [@somov2020]. The coastal LFS 7742 trawl net averaged `r coastalhigh` m high by `r coastalwide` m wide, or an area of `r round(coastalhigh * coastalwide)` m^2^, during surface tows on this survey. This mouth area is similar to a previous survey on the *FV Sea Crest* where the coastal LFS 7742 trawl net mouth opening averaged 19 m high by 41 m wide at the surface, or area of (779 m^2^; [@anderson2019]). All catch per unit effort (CPUE) reported here are standardized by swept volume to standardize catch values.

## CATCH COMPOSITION
```{r catchcomposition}

totalcatchkg <- round(sum(catch$totalWgt, na.rm = TRUE)/1000)

totalsalmon <- catch %>%
  filter(str_extract(SCIENTIFIC_NAME, "Oncorhynchus") == "Oncorhynchus")

totalsalmonkg <- round(sum(totalsalmon$totalWgt, na.rm = TRUE)/1000)

percentsalmon <- round(totalsalmonkg/totalcatchkg*100)

numSpecies <- nrow(catch)

abundantspeciesnames1 <- catch %>%
  slice(1:2) %>%
  pull(COMMON_NAME) %>%
  str_to_title() %>%
  first

abundantspeciesnames1kg <- catch %>%
  filter(str_to_title(COMMON_NAME) == abundantspeciesnames1) %>%
  mutate(totalWgtkg = round(totalWgt/1000)) %>%
  pull(totalWgtkg) 

abundantspeciesnames2 <- catch %>%
  slice(1:2) %>%
  pull(COMMON_NAME) %>%
  str_to_title() %>%
  last

abundantspeciesnames2kg <- catch %>%
  filter(str_to_title(COMMON_NAME) == abundantspeciesnames2) %>%
  mutate(totalWgtkg = round(totalWgt/1000)) %>%
  pull(totalWgtkg) 

abundantspeciesnames3 <- catch %>%
  slice(3:3) %>%
  pull(COMMON_NAME) %>%
  str_to_title() %>%
  last

abundantspeciesnames3kg <- catch %>%
  filter(str_to_title(COMMON_NAME) == abundantspeciesnames3) %>%
  mutate(totalWgtkg = round(totalWgt/1000)) %>%
  pull(totalWgtkg) 

```

For each of `r numSpecies` species captured during the survey, the number of tows in which the species was present, total catch weight, maximum catch weight, and mean catch weight per tow for usable tows is presented in Table \@ref(tab:catchtable). The most abundance species caught by weight were `r abundantspeciesnames1`, primarily caught in one set (`r abundantspeciesnames1kg` kg), `r abundantspeciesnames2` (`r abundantspeciesnames2kg` kg), then `r abundantspeciesnames3` (`r abundantspeciesnames3kg` kg; Table \@ref(tab:catchtable)). All species of juvenile Pacific Salmon were caught. The order of abundance by weight was Chum Salmon, Coho Salmon, Pink Salmon, Sockeye Salmon, and Chinook Salmon. Total catch for the survey from usable tows was `r totalcatchkg` kg, with `r totalsalmonkg` kg or `r percentsalmon`% Pacific Salmon. Detailed catch composition for each tow is included in Appendix \@ref(app:appCatch).

Chum Salmon were abundant in the northern portion the survey area, with the highest catches within Hecate Strait (Figure \@ref(fig:cmcpue)). Pink Salmon had the second highest abundance by count and were found throughout the survey area, except offshore (Figure \@ref(fig:pkcpue)). Juvenile Sockeye Salmon were strongly localized in the northern area of Dixon Entrance (Figure \@ref(fig:secpue)). Coho Salmon were primarily caught throughout Dixon Entrance, with lesser numbers in Hecate Strait (Figure \@ref(fig:cocpue)). Finally, there was only one Chinook Salmon caught during a usable tow in Hecate Strait (Figure \@ref(fig:ckcpue); not including the two Chinook Salmon caught during the aborted tow in Queen Charlotte Strait).

## BIOLOGICAL SAMPLES

Samples were collected for DNA stock composition (322), otoliths (322), energy density (259), stable isotope analysis (170), and coded wire tags (3). These biological samples are located at the Pacific Biological Station (Nanaimo, BC) awaiting laboratory analysis.

## LENGTH AND WEIGHT
```{r lengthandweight}

lwspeciesnum <- nrow(lw)

lwsalmon <- lw %>%
  filter(str_extract(COMMON_NAME, "Salmon") == "Salmon")

bigsalmon <- lwsalmon %>%
  arrange(-meanLen) %>%
  slice(1:1)

bigsalmonNam <- bigsalmon %>% pull(COMMON_NAME)
bigsalmonLen <- bigsalmon %>% pull(meanLen)
bigsalmonWGT <- bigsalmon %>% pull(meanWGT)

smlsalmon <- lwsalmon %>%
  arrange(meanLen) %>%
  slice(1:1)

smlsalmonNam <- str_to_title(smlsalmon %>% pull(COMMON_NAME))
smlsalmonLen <- smlsalmon %>% pull(meanLen)
smlsalmonWGT <- smlsalmon %>% pull(meanWGT)

```

Length frequencies and length-weight relationships are presented for Pacific Salmon species in Figures \@ref(fig:forkcm) to \@ref(fig:forkck). Double log transformed length-weight regressions coefficients were similar for all Pacific Salmon species, except Coho Salmon. The relationship between length and weight in juvenile Coho Salmon was more variable, with a smaller slope (Figure \@ref(fig:forkco)). Lengths and weights of `r lwspeciesnum` species were recorded, with all five Pacific Salmon species represented (Table \@ref(tab:lwtable)) `r bigsalmonNam` had the largest mean length (`r bigsalmonLen` mm) and weight (`r bigsalmonWGT` g), whereas `r smlsalmonNam` had the smallest mean length (`r smlsalmonLen` mm) and weight (`r smlsalmonWGT` g) of the Pacific Salmon species. These size differences are expected given the different life histories of Pacific Salmon species. For example, juvenile Pink Salmon migrate to the marine environment in their first year, whereas juvenile Coho Salmon migrate later and some individuals remain in the coastal environment [@quinn2018].

## STOMACH CONTENTS
```{r stomachcontents}

totalstomachs <- sum(stomachdf$NumStomachs)
totalstomachspecies <- nrow(stomachdf)

salmonstomachs <- stomachdf %>%
  filter(str_extract(COMMON_NAME, "Salmon") == "Salmon") %>%
  arrange(-PerEmpty)

ckstomach <- stomachdf %>%
  filter(COMMON_NAME == "Chinook Salmon") %>%
  pull(PerEmpty)

costomach <- stomachdf %>%
  filter(COMMON_NAME == "Coho Salmon") %>%
  pull(PerEmpty)

cmstomach <- stomachdf %>%
  filter(COMMON_NAME == "Chum Salmon") %>%
  pull(PerEmpty)

pkstomach <- stomachdf %>%
  filter(COMMON_NAME == "Pink Salmon") %>%
  pull(PerEmpty)

sestomach <- stomachdf %>%
  filter(COMMON_NAME == "Sockeye Salmon") %>%
  pull(PerEmpty)

```

Stomachs of `r totalstomachs` individual fish, from `r totalstomachspecies` species, were analysed at sea (Table \@ref(tab:stomachtable)). Chinook Salmon (`r ckstomach`%) and Coho Salmon (`r costomach`%) had the highest percentage of empty stomachs, whereas Chum Salmon (`r cmstomach`%) had the lowest percentage of empty stomach within Pacific Salmon species. Pink Salmon (`r pkstomach`%) and Sockeye Salmon (`r sestomach`%) had intermediate percentages of empty stomachs (Table \@ref(tab:stomachtable)). 

Juvenile Pacific Salmon showed species-specific differences in their prey items (Table \@ref(tab:preytable)). Juvenile Chum Salmon primarily had unidentified remains within their stomachs. Jellyfish and Squid are digested quickly; therefore, unidentified remains may represents those prey species. Juvenile Coho Salmon showed the widest range of prey species. The most common prey within juvenile Pink Salmon and Sockeye Salmon stomachs were amphipods and euphausiids. The only Chinook Salmon with stomach contents contained Squid (Table \@ref(tab:preytable)).

## OCEANOGRAPHY
```{r oceanography}

ctdnum <- ocean_orig %>%
  filter(Type %in% c("CTD", "ROS"))

ctdmaxdepth <- max(ctdnum$CastDepth)
ctdmindepth <- min(ctdnum$CastDepth)
  
```

CTD casts and water samples were completed at `r nrow(ctdnum)` sites with cast depths ranging from `r ctdmindepth` m to `r ctdmaxdepth` m (Appendix \@ref(app:appOcean)). Samples were collected for nutrients and chlorophyll, primarily at surface with some limited ligand sampling at depth during the CTD rosette operations. The LARS was used to launch the rosette with the Seabird 911 CTD for the first two stations (CS01, T01). Thereafter, a standalone Seabird 25 CTD was deployed. Oceanographic data from the CTD rosette and standalone CTD casts, including water samples for nitrate, phosphate, silicate, and chl a, are being processed, analyzed, and will be archived online within the [Water Properties Data Inventory](https://www.waterproperties.ca). 

## ZOOPLANKTON
```{r planktonresults}

planktonvert <- ocean_orig %>%
  filter(Type == "BongoVertical")

planktonmax <- max(planktonvert$CastDepth)
planktonmin <- min(planktonvert$CastDepth)

```

Vertical bongo tows were conducted at `r nrow(planktonvert)` stations to depths ranging from `r planktonmin` m to `r planktonmax` m (Appendix \@ref(app:appOcean)). Formalin-preserved zooplankton samples will be identified and enumerated at the Institute of Ocean Sciences (Sidney, BC). Data will be archived in the zooplankton database. Fractionated zooplankton samples are frozen at the Pacific Biological Station (Nanaimo, BC).

In preparation for the 2022 Pan-Pacific High Seas Expedition, three MOCNESS and two oblique bongo tows were completed. Both techniques were deployed under calm sea conditions off the *`r vessel`*. The MOCNESS did not close nets between all depth strata in 2 of the 3 tows. This failure to release the nets is being investigated. 

## ACOUSTIC DATA
Acoustic data was collected throughout the survey with the drop keel deployed, for analysis at the Institute of Ocean Sciences, Fisheries and Oceans Canada (Sidney, BC).
