# FIGURES

(ref:mapfish) Fishing tow locations during the `r surveyName` from `r surveyDateRange` on the `r vessel`. The LFS 7742 coastal trawl net (red triangles) was used for 20 tows and the LFS 1142 offshore trawl net (orange circles) was used for 2 tows.

```{r mapfish, fig.pos="H", fig.cap = "(ref:mapfish)", warning=FALSE}

events_fish <- events %>%
  mutate(Gear = str_extract(Type, "[0-9]+"),
         Test = str_extract(Comments, "DO NOT USE")) %>%
  filter(!(is.na(Gear))) %>%
  filter(is.na(Test))
  
  basemap +
    geom_point(data = events_fish,
             aes(Start_Long_DD, Start_Lat_DD, shape = Type, color = Type),
             size = 3) +
    scale_color_manual(values = c("orange", "darkred")) +
    theme(legend.position = "none")


```

(ref:mapctd) Oceanographic sampling locations during the `r surveyName` from `r surveyDateRange` on the `r vessel`. There were 19 Seabird 25 CTD casts (red circles) and 2 Seabird 911 rosette casts (orange triangles).

```{r mapctd, fig.pos="H", fig.cap = "(ref:mapctd)", warning=FALSE}

events_ctd <- events %>%
  filter(Type == "ROS" | Type == "CTD")
  
  basemap +
    geom_point(data = events_ctd,
             aes(Start_Long_DD, Start_Lat_DD, shape = Type, color = Type),
             size = 3) +
    scale_color_manual(values = c("darkred", "orange")) +
    theme(legend.position = "none")
  

```

(ref:mapplankton) Plankton sampling locations during the `r surveyName` from `r surveyDateRange` on the `r vessel`. There were 21 vertical plankton tows (red triangles), 2 oblique plankton tows (yellow circles) and 3 MOCNESS tows (black squares).

```{r mapplankton, fig.pos="H", fig.cap = "(ref:mapplankton)", warning=FALSE}

events_bongoVert <- events %>%
  filter(Type == "BongoVertical")

events_bongoObliq <- events %>%
  filter(Type == "BongoOblique")

events_mocness <- events %>%
  filter(Type == "MOCNESS")
  
  basemap +
    geom_point(data = events_mocness,
             aes(Start_Long_DD, Start_Lat_DD),
             shape = 15,
             color = "black",
             size = 5) +
    geom_point(data = events_bongoObliq,
             aes(Start_Long_DD, Start_Lat_DD),
             shape = 16,
             color = "orange",
             size = 4) +
    geom_point(data = events_bongoVert,
             aes(Start_Long_DD, Start_Lat_DD),
             shape = 17,
             color = "darkred",
             size = 3)
  
```

(ref:cmcpue) Juvenile chum salmon (*Oncorhynchus keta*) catch per km^3^ per tow. Red circles are proportional to catch abundance, and zero catches are shown with a cross (+).

```{r cmcpue, fig.pos="H", fig.cap = "(ref:cmcpue)", warning=FALSE}

# wrangle data for specific species
cmcpue <- salmondf %>%
    filter(CM_JUV != 0) %>%
  select(EVENT, START_LAT, START_LONG, `ESTIMATED_CATCHES_ BY_WT`, CM_JUV_KM3)

# df for zero catch
cmzero <- salmondf %>%
  filter(CM_JUV == 0) %>%
    select(EVENT, START_LAT, START_LONG, CM_JUV_KM3)

# map cpue
basemap +
  geom_point(data = cmcpue,
             aes(START_LONG, START_LAT, size = CM_JUV_KM3),
             color = "darkred") +
    geom_point(data = cmzero,
             aes(START_LONG, START_LAT),
             shape = 3) +
  labs(size = "Juveniles \n per km3") 

```

(ref:pkcpue) Juvenile pink salmon (*Oncorhynchus gorbusha*) catch per km^3^ per tow. Red circles are proportional to catch abundance, and zero catches are shown with a cross (+).

```{r pkcpue, fig.pos="H", fig.cap = "(ref:pkcpue)", warning=FALSE}

# wrangle data for specific species
pkcpue <- salmondf %>%
    filter(PK_JUV != 0) %>%
  select(EVENT, START_LAT, START_LONG, `ESTIMATED_CATCHES_ BY_WT`, PK_JUV_KM3)

# df for zero catch
pkzero <- salmondf %>%
  filter(PK_JUV == 0) %>%
    select(EVENT, START_LAT, START_LONG, PK_JUV_KM3)

# map cpue
basemap +
  geom_point(data = pkcpue,
             aes(START_LONG, START_LAT, size = PK_JUV_KM3),
             color = "darkred") +
    geom_point(data = pkzero,
             aes(START_LONG, START_LAT),
             shape = 3) +
  labs(size = "Juveniles \n per km3") 

```


(ref:secpue) Juvenile sockeye salmon (*Oncorhynchus nerka*) catch per km^3^ per tow. Red circles are proportional to catch abundance, and zero catches are shown with a cross (+).

```{r secpue, fig.pos="H", fig.cap = "(ref:secpue)", warning=FALSE}

# wrangle data for specific species
secpue <- salmondf %>%
    filter(SE_JUV != 0) %>%
  select(EVENT, START_LAT, START_LONG, `ESTIMATED_CATCHES_ BY_WT`, SE_JUV_KM3)

# df for zero catch
sezero <- salmondf %>%
  filter(SE_JUV == 0) %>%
    select(EVENT, START_LAT, START_LONG, SE_JUV_KM3)

# map cpue
basemap +
  geom_point(data = secpue,
             aes(START_LONG, START_LAT, size = SE_JUV_KM3),
             color = "darkred") +
    geom_point(data = sezero,
             aes(START_LONG, START_LAT),
             shape = 3) +
  labs(size = "Juveniles \n per km3") 

```

(ref:cocpue) Juvenile coho salmon (*Oncorhynchus kitsutch*) catch per km^3^ per tow. Red circles are proportional to catch abundance, and zero catches are shown with a cross (+).

```{r cocpue, fig.pos="H", fig.cap = "(ref:cocpue)", warning=FALSE}

# wrangle data for specific species
cocpue <- salmondf %>%
    filter(CO_JUV != 0) %>%
  select(EVENT, START_LAT, START_LONG, `ESTIMATED_CATCHES_ BY_WT`, CO_JUV_KM3)

# df for zero catch
cozero <- salmondf %>%
  filter(CO_JUV == 0) %>%
    select(EVENT, START_LAT, START_LONG, CO_JUV_KM3)

# map cpue
basemap +
  geom_point(data = cocpue,
             aes(START_LONG, START_LAT, size = CO_JUV_KM3),
             color = "darkred") +
    geom_point(data = cozero,
             aes(START_LONG, START_LAT),
             shape = 3) +
  labs(size = "Juveniles \n per km3") 

``` 

(ref:ckcpue) Juvenile chinook salmon (*Oncorhynchus tschawytscha*) catch per km^3^ per tow. Red circles are proportional to catch abundance, and zero catches are shown with a cross (+).

```{r ckcpue, fig.pos="H", fig.cap = "(ref:ckcpue)", warning=FALSE}

# wrangle data for specific species
ckcpue <- salmondf %>%
    filter(CK_JUV != 0) %>%
  select(EVENT, START_LAT, START_LONG, `ESTIMATED_CATCHES_ BY_WT`, CK_JUV_KM3)

# df for zero catch
ckzero <- salmondf %>%
  filter(CK_JUV == 0) %>%
    select(EVENT, START_LAT, START_LONG, CK_JUV_KM3)

# map cpue
basemap +
  geom_point(data = ckcpue,
             aes(START_LONG, START_LAT, size = CK_JUV_KM3),
             color = "darkred") +
    geom_point(data = ckzero,
             aes(START_LONG, START_LAT),
             shape = 3) +
  labs(size = "Juveniles \n per km3") +
  scale_size_continuous(labels = c(420))

```

(ref:forkcm) Juveile chum salmon (*Oncorhynchus keta*) length frequency plot as sampled during the `r surveyName` aboard the `r vessel`, `r surveyDateRange` (A). Double log-transformed length-weight regression with outliers removed, using a Bonferroni outlier test (B).

```{r forkcm, fig.cap="(ref:forkcm)"}

### create function to repeat graphs on different species
graphSpecies <- function(lengthFreq, thisspecies) {

# select species
thisdf <- filter(lengthFreq, COMMON_NAME == thisspecies)

##### Removing Length-Weight outliers
#### L-W Regression- there are more lengths than weights so remove NA weights
df.LW <- thisdf %>%
  filter(!is.na(WEIGHT)) %>%
  filter(!is.na(LENGTH)) %>%
  dplyr::select(., c(TRIP_ID, LENGTH, WEIGHT, LOG.LEN, LOG.WT))

### Regression model
df.LWReg <- lm(LOG.WT~LOG.LEN, data = df.LW)
df.LW$LWResids <- resid(df.LWReg)

## Produce Bonferoni value for each point in your data
test.df.LW <- outlierTest(df.LWReg, n.max = Inf, cutoff = Inf, order = FALSE)$bonf.p
df.LWremove <- which(test.df.LW < .7)

# EA: modified to account for no outliers in species
if (length(df.LWremove) > 0) {
  df.LW <- df.LW[-df.LWremove, ]
}

# EA: changed code to plot with ggplot

# graph length frequency
dfbar <- ggplot(df.LW) +
  geom_histogram(aes(LENGTH), binwidth = 5) +
  labs(x = "Length (mm)",
       y = "Count") +
  theme_bw()


# create function to print equation for the LW regression
lm_eqn <- function(df){

  # get model without outliers
dfmodel <- lm(LOG.WT~LOG.LEN, df)

  # make model into tidy data frame
  tidy(dfmodel)

  # make equation text from values in model
    eq <- substitute(italic(y) == a + b *italic(x)*","~italic(R)^2~"="~r2~","~p,
         list(a = format(unname(dfmodel$coefficients[1]), digits = 2),
              b = format(unname(dfmodel$coefficients[2]), digits = 2),
             r2 = round(glance(dfmodel)$r.squared, 3),
              p = if_else(round(glance(dfmodel)$p.value, 3) == 0, "p-value < 0.001", paste0("p-value = ", as.character(round(glance(dfmodel)$p.value, 3))))))
    as.character(as.expression(eq));
}
lm_text <- lm_eqn(df.LW)

# calculate where equation test should go
xtext <- ((max(df.LW$LOG.LEN) - min(df.LW$LOG.LEN))/3)*2 + min(df.LW$LOG.LEN)
ytext <- ((max(df.LW$LOG.WT) - min(df.LW$LOG.WT))/2) + min(df.LW$LOG.WT) - 1

if(thisspecies == "CHINOOK") { # remove equations in 2020017 since only three CK caught
# graph log length by weight
dffit <- ggplot(df.LW) +
  geom_point(aes(LOG.LEN, LOG.WT)) +
  labs(x = "log(Length (mm))",
       y = "log(Weight (g))") +
  #geom_text(aes(xtext, ytext), label = lm_text, parse = TRUE) +
  theme_bw()
} else {
  
  # graph log length by weight
dffit <- ggplot(df.LW) +
  geom_point(aes(LOG.LEN, LOG.WT)) +
  labs(x = "log(Length (mm))",
       y = "log(Weight (g))") +
  geom_text(aes(xtext, ytext), label = lm_text, parse = TRUE) +
  theme_bw()
  
}

# put both graphs in list to return from function
list(dfbar, dffit)

}

# remove adult chum since there were only two and no other adult salmon sampled
lengthFreqCmJuv <- lengthFreq %>%
  filter(LENGTH < 500)

# create graphs 
chumList <- graphSpecies(lengthFreqCmJuv, "CHUM")
chumbar <- chumList[[1]]
chumLine <- chumList[[2]]
chumPlots <- plot_grid(chumbar, chumLine, ncol = 1,
                          labels = c('A', 'B'), label_size = 12)
chumPlots

```

(ref:forkpk) Juveile pink salmon (*Oncorhynchus gorbusha*) length frequency plot as sampled during the `r surveyName` aboard the `r vessel`, `r surveyDateRange` (A). Double log-transformed length-weight regression with outliers removed, using a Bonferroni outlier test (B).

```{r forkpk, fig.cap="(ref:forkpk)"}

pinkList <- graphSpecies(lengthFreq, "PINK")
pinkbar <- pinkList[[1]]
pinkLine <- pinkList[[2]]
pinkPlots <- plot_grid(pinkbar, pinkLine, ncol = 1,
                          labels = c('A', 'B'), label_size = 12)
pinkPlots

```

(ref:forkse) Juvenile sockeye salmon (*Oncorhynchus nerka*) length frequency plot as sampled during the `r surveyName` aboard the `r vessel`, `r surveyDateRange` (A). Double log-transformed length-weight regression with outliers removed, using a Bonferroni outlier test (B).

```{r forkse, fig.cap="(ref:forkse)"}

sockeyeList <- graphSpecies(lengthFreq, "SOCKEYE")
sockeyebar <- sockeyeList[[1]]
sockeyeLine <- sockeyeList[[2]]
sockeyePlots <- plot_grid(sockeyebar, sockeyeLine, ncol = 1,
                          labels = c('A', 'B'), label_size = 12)
sockeyePlots

```

(ref:forkco) Juvenile coho salmon (*Oncorhynchus kisutch*) length frequency plot as sampled during the `r surveyName` aboard the `r vessel`, `r surveyDateRange` (A). Double log-transformed length-weight regression with outliers removed, using a Bonferroni outlier test (B).

```{r forkco, fig.cap="(ref:forkco)"}

cohoList <- graphSpecies(lengthFreq, "COHO")
cohobar <- cohoList[[1]]
cohoLine <- cohoList[[2]]
cohoPlots <- plot_grid(cohobar, cohoLine, ncol = 1,
                          labels = c('A', 'B'), label_size = 12)
cohoPlots

```

(ref:forkck) Juvenile chinook salmon (*Oncorhynchus tshawytscha)*) length frequency plot as sampled during the `r surveyName` aboard the `r vessel`, `r surveyDateRange` (A). Double log-transformed length-weight regression with outliers removed, using a Bonferroni outlier test (B). No linear equation is presented since there were too few caught.

```{r forkck, fig.cap="(ref:forkck)"}

chinookList <- graphSpecies(lengthFreq, "CHINOOK")
chinookbar <- chinookList[[1]]
chinookLine <- chinookList[[2]]
chinookPlots <- plot_grid(chinookbar, chinookLine, ncol = 1,
                          labels = c('A', 'B'), label_size = 12)
chinookPlots

```

\FloatBarrier
\newpage