# Figures

(ref:mapfish) Fishing locations during the `r surveyName` from `r surveyDateRange` on the `r vessel`. The LFS 7742 coastal trawl net (red triangles) was used for 20 tows and the LFS 1142 offshore trawl net (orange circles) was used for 2 tows.

```{r mapfish, fig.pos="H", fig.cap = "(ref:mapfish)", warning=FALSE}

events_fish <- events %>%
  mutate(Gear = str_extract(Type, "[0-9]+"),
         Test = str_extract(Comments, "DO NOT USE")) %>%
  filter(!(is.na(Gear))) %>%
  filter(is.na(Test))
  
  basemap +
    geom_point(data = events_fish,
             aes(Start_Long_DD, Start_Lat_DD, shape = Type, color = Type),
             size = 3) +
    scale_color_manual(values = c("orange", "darkred")) +
    theme(legend.position = "none")


```

(ref:mapctd) Oceanographic sampling locations during the `r surveyName` from `r surveyDateRange` on the `r vessel`. There were 19 Seabird 25 CTD casts (red circles) and 2 Seabird 911 rosette casts (orange triangles).

```{r mapctd, fig.pos="H", fig.cap = "(ref:mapctd)", warning=FALSE}

events_ctd <- events %>%
  filter(Type == "ROS" | Type == "CTD")
  
  basemap +
    geom_point(data = events_ctd,
             aes(Start_Long_DD, Start_Lat_DD, shape = Type, color = Type),
             size = 3) +
    scale_color_manual(values = c("darkred", "orange")) +
    theme(legend.position = "none")
  

```

(ref:mapplankton) Zooplankton sampling locations during the `r surveyName` from `r surveyDateRange` on the `r vessel`. There were 21 vertical plankton tows (red triangles), 2 oblique plankton tows (yellow circles) and 3 MOCNESS tows (black squares).

```{r mapplankton, fig.pos="H", fig.cap = "(ref:mapplankton)", warning=FALSE}

events_bongoVert <- events %>%
  filter(Type == "BongoVertical")

events_bongoObliq <- events %>%
  filter(Type == "BongoOblique")

events_mocness <- events %>%
  filter(Type == "MOCNESS")
  
  basemap +
    geom_point(data = events_mocness,
             aes(Start_Long_DD, Start_Lat_DD),
             shape = 15,
             color = "black",
             size = 5) +
    geom_point(data = events_bongoObliq,
             aes(Start_Long_DD, Start_Lat_DD),
             shape = 16,
             color = "orange",
             size = 4) +
    geom_point(data = events_bongoVert,
             aes(Start_Long_DD, Start_Lat_DD),
             shape = 17,
             color = "darkred",
             size = 3)
  
```


(ref:cmcpue) Juvenile chum salmon (*Oncorhynchus keta*) catch in thousand of individuals per km^3^ per tow. Red circles are proportional to catch abundance, and zero catches are shown with a cross (+).

```{r cmcpue, fig.pos="H", fig.cap = "(ref:cmcpue)", warning=FALSE}

# wrangle data for specific species
cmcpue <- salmondf %>%
    filter(CM_JUV != 0) %>%
  select(EVENT, START_LAT, START_LONG, `ESTIMATED_CATCHES_ BY_WT`, CM_JUV_KM3)

# df for zero catch
cmzero <- salmondf %>%
  filter(CM_JUV == 0) %>%
    select(EVENT, START_LAT, START_LONG, CM_JUV_KM3)

# map cpue
basemap +
  geom_point(data = cmcpue,
             aes(START_LONG, START_LAT, size = CM_JUV_KM3),
             color = "darkred") +
    geom_point(data = cmzero,
             aes(START_LONG, START_LAT),
             shape = 3) +
  labs(size = "Juveniles \n per km3") 

```

(ref:pkcpue) Juvenile pink salmon (*Oncorhynchus gorbusha*) catch in thousand of individuals per km^3^ per tow. Red circles are proportional to catch abundance, and zero catches are shown with a cross (+).

```{r pkcpue, fig.pos="H", fig.cap = "(ref:pkcpue)", warning=FALSE}

# wrangle data for specific species
pkcpue <- salmondf %>%
    filter(PK_JUV != 0) %>%
  select(EVENT, START_LAT, START_LONG, `ESTIMATED_CATCHES_ BY_WT`, PK_JUV_KM3)

# df for zero catch
pkzero <- salmondf %>%
  filter(PK_JUV == 0) %>%
    select(EVENT, START_LAT, START_LONG, PK_JUV_KM3)

# map cpue
basemap +
  geom_point(data = pkcpue,
             aes(START_LONG, START_LAT, size = PK_JUV_KM3),
             color = "darkred") +
    geom_point(data = pkzero,
             aes(START_LONG, START_LAT),
             shape = 3) +
  labs(size = "Juveniles \n per km3") 

```


(ref:secpue) Juvenile sockeye salmon (*Oncorhynchus nerka*) catch in thousand of individuals per km^3^ per tow. Red circles are proportional to catch abundance, and zero catches are shown with a cross (+).

```{r secpue, fig.pos="H", fig.cap = "(ref:secpue)", warning=FALSE}

# wrangle data for specific species
secpue <- salmondf %>%
    filter(SE_JUV != 0) %>%
  select(EVENT, START_LAT, START_LONG, `ESTIMATED_CATCHES_ BY_WT`, SE_JUV_KM3)

# df for zero catch
sezero <- salmondf %>%
  filter(SE_JUV == 0) %>%
    select(EVENT, START_LAT, START_LONG, SE_JUV_KM3)

# map cpue
basemap +
  geom_point(data = secpue,
             aes(START_LONG, START_LAT, size = SE_JUV_KM3),
             color = "darkred") +
    geom_point(data = sezero,
             aes(START_LONG, START_LAT),
             shape = 3) +
  labs(size = "Juveniles \n per km3") 

```

(ref:cocpue) Juvenile coho salmon (*Oncorhynchus kitsutch*) catch in thousand of individuals per km^3^ per tow. Red circles are proportional to catch abundance, and zero catches are shown with a cross (+).

```{r cocpue, fig.pos="H", fig.cap = "(ref:cocpue)", warning=FALSE}

# wrangle data for specific species
cocpue <- salmondf %>%
    filter(CO_JUV != 0) %>%
  select(EVENT, START_LAT, START_LONG, `ESTIMATED_CATCHES_ BY_WT`, CO_JUV_KM3)

# df for zero catch
cozero <- salmondf %>%
  filter(CO_JUV == 0) %>%
    select(EVENT, START_LAT, START_LONG, CO_JUV_KM3)

# map cpue
basemap +
  geom_point(data = cocpue,
             aes(START_LONG, START_LAT, size = CO_JUV_KM3),
             color = "darkred") +
    geom_point(data = cozero,
             aes(START_LONG, START_LAT),
             shape = 3) +
  labs(size = "Juveniles \n per km3") 

``` 

(ref:ckcpue) Juvenile chinook salmon (*Oncorhynchus tschawytscha*) catch in thousand of individuals per km^3^ per tow. Red circles are proportional to catch abundance, and zero catches are shown with a cross (+).

```{r ckcpue, fig.pos="H", fig.cap = "(ref:ckcpue)", warning=FALSE}

# wrangle data for specific species
ckcpue <- salmondf %>%
    filter(CK_JUV != 0) %>%
  select(EVENT, START_LAT, START_LONG, `ESTIMATED_CATCHES_ BY_WT`, CK_JUV_KM3)

# df for zero catch
ckzero <- salmondf %>%
  filter(CK_JUV == 0) %>%
    select(EVENT, START_LAT, START_LONG, CK_JUV_KM3)

# map cpue
basemap +
  geom_point(data = ckcpue,
             aes(START_LONG, START_LAT, size = CK_JUV_KM3),
             color = "darkred") +
    geom_point(data = ckzero,
             aes(START_LONG, START_LAT),
             shape = 3) +
  labs(size = "Juveniles \n per km3") +
  scale_size_continuous(labels = c(420))

```

Length frequencies and log length to weight regression (all species?)     

Bell diameters for > 100 individuals?    

