# Tables

(ref:totaltows) Total usable fishing, CTD, plankton, and MOCNESS events during the `r surveyName` aboard the `r vessel`, `r surveyDateRange`. Gear testing and aborted tows are not included in this table. Please see methods section for more detailed equipment information.

```{r totaltows, results = 'asis'}

tows <- tibble(
  Event = c("Coastal LFS 7742 Midwater Trawl", "Offshore LFS 1142 Midwater Trawl", "CTD Seabird 25", "Rosette with Seabird 911", "Vertical Plankton Tow", "Oblique Plankton Tow", "MOCNESS"),
  "Number Usable" = c(20, 2, 19, 2, 21, 2, 3))

# csasdown::csas_table(tows,
#                      caption = "(ref:totaltows)")

```
\newpage
  

(ref:catchtable) All captured species (or taxonomic group), ordered by total catch weight (in grams), showing number of tows in which the species occurred, total catch weight, maximum catch weight, and mean catch weight per tow for usable tows during the `r surveyName` aboard the `r vessel`, `r surveyDateRange`. Blank weights indicate specimens which could not be weighed accurately (either released alive or too small).

```{r catchtable, results='asis'}
csasdown::csas_table(catch,
                     #format = "latex",
                     caption = "(ref:catchtable)",
                     col.names = c("Common Name", "Scientific Name","Tows", "Total", "Max", "Mean")) 
# %>%
#     kableExtra::kable_styling(font_size = 8, latex_options = "repeat_header",
#      repeat_header_text = "continued.", repeat_header_method = "replace") %>%
#   add_header_above(c("", "", "", "Catch (g)" = 3)) %>%
#   row_spec(vertline, hline_after = T) 
```
  
  
(ref:lwtable) Lengths (mm) and weights (g) for each species (arranged decending by the number of tows for each by species) sampled during the `r surveyName` aboard the `r vessel`, `r surveyDateRange`. (Tows = number of tows, Measured = number of lengths, Weighed = number of weights).

```{r lwtable, results='asis'}

csasdown::csas_table(lw,
                     # format = "Latex",
                     caption = "(ref:lwtable)",
                     col.names = c("Species", "Tows","Measured", "MeanL", "MinL", "MaxL", "Weighed", "MeanW", "MinW", "MaxW"))
        
  #       col.names = c("Species", "Tows", "Measured", "Mean", "Min", "Max", "Weighed", "Mean", "Min", "Max"),
  #       col_names_align = "c") %>%
  # kableExtra::add_header_above(c("", "", "", "Length (mm)" = 3, "", "Weight (g)" = 3)) %>%
  # kableExtra::column_spec(column = 1, width = "3cm")

```
  
  
(ref:stomachtable) Number of tows with samples, number of stomachs examined, number of empty stomachs, and percentage of empty stomachs for each species (arranged descending by number of tows) during the `r surveyName` aboard the `r vessel`, `r surveyDateRange`.
  
```{r stomachtable, results = 'asis'}

csasdown::csas_table(stomachdf,
                     caption = "(ref:stomachtable)",
        col.names = c("Species", "Tows", "Stomachs", "Empty", "Percent"),
  col_names_align = "c")
#%>%
#   column_spec(column = 1, width = "4 cm") %>%
#   column_spec(column = 2, width = "1.8 cm") %>%
#   column_spec(column = 3, width = "1.8 cm") %>%
#   column_spec(column = 4, width = "1.8 cm") %>%
#   column_spec(column = 5, width = "1.8 cm"
#   )

```
\newpage
  
  
(ref:preytable) Prey items identified in the stomach contents of species sampled (list alphebetically) during during the `r surveyName` aboard the `r vessel`, `r surveyDateRange`. Volume is averaged in cm^3^; Count is the number of stomachs observed with this prey.
  
```{r preytable, results = 'asis'}

csasdown::csas_table(prey,
                     caption = "(ref:preytable)",
  col.names = c("Species", "Prey", "Volume", "Count"),
  col_names_align = "c")  

# %>%
#   column_spec(column = 1, width = "4 cm") %>%
#   column_spec(column = 2, width = "4 cm") %>%
#   column_spec(column = 3, width = "2 cm") %>%
#   column_spec(column = 4, width = "2 cm"
# )

```

