# Tables

(ref:totaltows) Total usable fishing, CTD, zooplankton, and MOCNESS events during the `r surveyName` aboard the `r vessel`, `r surveyDateRange`. Test and aborted tows are not included in this table. Please see methods section for more detailed equipment information.

```{r totaltows, results = 'asis'}

tows <- tibble(
  Event = c("Midwater Coastal Trawl", "Midwater Offshore Trawl", "CTD Seabird 25", "Rosette with Seabird 911", "Vertical Zooplankton Tow", "Oblique Zooplankton Tow", "MOCNESS"),
  Number = c(20, 2, 19, 2, 21, 2, 3))

csasdown::csas_table(tows,
                     caption = "(ref:totaltows)")

```

  
(ref:catchtable) All captured species (or taxonomic group), ordered by total catch weight, showing number of tows in which the species occurred, total catch weight, maximum catch weight, and mean catch weight per tow for usable tows during the `r surveyName` aboard the `r vessel`, `r surveyDateRange`. Blank weights indicate specimens that could not be weighed accurately (either released alive or too small).

```{r catchtable, results='asis'}
csasdown::csas_table(catch,
                     caption = "(ref:catchtable)",
                     col.names = c("Common Name", "Scientific Name","Tows", "Total", "Max", "Mean"))
```
  
  
Species Lengths and Weights  
Sample size and statistics of lengths and weights for each species (listed
alphabetically) sampled during the `r surveyName` aboard the `r vessel`, `r surveyDateRange`. (Sampled = number of tows, Measured = number of lengths, Weighed = number of weights).

Stomach Table
Number of samples (tows), number of stomachs examined, number empty
stomachs, and percentage of stomachs that were empty for species sampled (listed
alphabetically) during the `r surveyName` aboard the `r vessel`, `r surveyDateRange`.  

Prey Table  
Prey items identified in the stomach contents of species sampled (listed
alphabetically) during during the `r surveyName` aboard the `r vessel`, `r surveyDateRange`. The average prey volume is in cm3 and the count of stomachs is the number of stomachs examined.  
  
