<!-- The following code should appear at the beginning of the first appendix.
After that, all subsequent sections will be turned into appendices. -->

`r if(knitr:::is_latex_output()) '% begin csasdown appendix'`
`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

\clearpage

# THE FIRST APPENDIX {#app:first-appendix}

Bridge Log table (landscape hard to do in word)
  
Catch Table  


(ref:test1) English version of the test1 figure caption

```{r test1, fig.cap="(ref:test1)"}
plot(1)
```

(ref:test1b) English version of the test1b figure caption

```{r test1b, results='asis'}
csasdown::csas_table(data.frame(x = c("a", "a", "b"),
                                y = c(1, 2, 3)),
                     caption = "English verion of the test2b table caption")
```

And references to them...

See Figure \@ref(fig:test1) for the example appendix figure.

See Table \@ref(tab:test1b) for the example appendix table.

\clearpage

# THE SECOND APPENDIX, FOR FUN {#app:second-appendix}

Tow plots?


<!-- At the end of your appendices add: -->
`r if(knitr:::is_latex_output()) '% end csasdown appendix'`
