<!-- The following code should appear at the beginning of the first appendix.
After that, all subsequent sections will be turned into appendices. -->

`r if(knitr:::is_latex_output()) '% begin csasdown appendix'`
`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

\clearpage

# THE FIRST APPENDIX {#app:nets}

Bridge Log table (landscape hard to do in word)
  
Catch Table  


(ref:offshorenet) Net specifications for the offshore NPAFC 1142 midwater trawl net used on the the `r surveyName` from `r surveyDateRange` on the `r vessel`.

```{r offshorenet, fig.cap="(ref:offshorenet)"}

# png of net specs

```

(ref:coastalnet) Net specifications for the coastal NPAFC 7742 midwater trawl net the `r surveyName` from `r surveyDateRange` on the `r vessel`.

```{r coastalnet, results='asis'}

# coastal net specs

```

\clearpage

# THE SECOND APPENDIX, FOR FUN {#app:second-appendix}

Tow plots?


<!-- At the end of your appendices add: -->
`r if(knitr:::is_latex_output()) '% end csasdown appendix'`
